### 2016-09-07 GPCE2016/sections/CaseStudy.tex
address reviews

Our refactoring applies the pattern presented in
Section~\ref{subsec:ep} to the existing Mumbler code base to improve
its modularity and extensibility. Using the refactored code base it
becomes possible to add new operations modularly, and to support
independent extensibility. We add one more
operation \texttt{print} to both the original and the refactored code
base. In the original code base the pretty printer is added
non-modularly by modifying the existing code. In the refactored code
base the pretty printer is added modularly. 
Although the code in the refactored version is slightly increased (by 2.4\% SLOC), the
modularity is greatly increased, allowing for improved reusability and maintainability:

>>>>

Our refactoring applies the pattern presented in
Section~\ref{subsec:ep} to the existing Mumbler code base to improve
its modularity and extensibility. Using the refactored code base it
becomes possible to add new operations modularly, and to support
independent extensibility. We add one more
operation \texttt{print} to both the original and the refactored code
base. In the original code base the pretty printer is added
non-modularly by modifying the existing code. In the refactored code
base, the pretty printer is added modularly with more interfaces, thus 
the code is slightly increased by 2.4\% SLOC. However, the
modularity is greatly increased, allowing for improved reusability and maintainability:

### 2016-09-07 GPCE2016/sections/Introduction.tex
address reviews

Object interfaces provide support for automatic type-refinement.  In
contrast, in CB special care and verbose explicit type-refinement are
required to produce code that deals with subtyping adequately. We
believe that such verbosity hindered and slowed down the discovery of
useful programming patterns involving type-refinement. A recently
discovered solution~\cite{eptrivially} to the Expression
Problem~\cite{wadler98expression} in Java-like languages shows how
easy it is to solve the problem using only type-refinement. However it
took nearly 20 years since the formulation of the problem for that
solution to be presented in the literature. In IB, due to its emphasis
on type-refinement, that solution should have been more obvious.

@@

Using Java annotation processors, we produce an implementation of
Classless Java, which allows us to stick to pure Java 8. By annotating
 the interfaces that represent object interfaces with \mixin, code for interface instantiation and
type refinement can be automatically generated. Such code should not be needed in the first place in
a real IB language, and the annotation processor allows us to
transparently hide it from Java programmers. The implementation works
by performing AST rewriting, allowing most existing Java tools (such as
IDEs) to work out-of-the-box with our implementation. Moreover, the
implementation blends Java's conventional CB style and IB smoothly.
As a result, we experiment object interfaces with several interesting
Java programs and conduct various case studies.  Finally, we also
discuss the behaviour of our \mixin annotation and
its properties.

>>>>

Object interfaces provide support for automatic type-refinement.  In
contrast, in CB special care and verbose explicit type-refinement are
required to produce code that deals with subtyping adequately. We
believe that such verbosity hindered and slowed down the discovery of
useful programming patterns involving type-refinement. Our previous work~\cite{eptrivially} 
on the Expression Problem~\cite{wadler98expression} in Java-like languages shows how
easy it is to solve the problem using only type-refinement. However it
took nearly 20 years since the formulation of the problem for that
solution to be presented in the literature. In IB, due to its emphasis
on type-refinement, that solution should have been more obvious.

@@

Using Java annotation processors, we produce an implementation of
Classless Java, which allows us to stick to pure Java 8. By annotating
 the interfaces that represent object interfaces with \mixin, code for interface instantiation and
type refinement can be automatically generated. Such code should not be needed in the first place in
a real IB language, and the annotation processor allows us to
transparently hide it from Java programmers. The implementation works
by performing AST rewriting, allowing most existing Java tools (such as
IDEs) to work out-of-the-box with our implementation. Moreover, the
implementation blends Java's conventional CB style and IB smoothly.
As a result, we apply object interfaces to several interesting
Java programs and conduct various case studies. Finally, we also
discuss the behaviour of our \mixin annotation and
its properties.
